Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-08-26 doc/paper.Rmd
move flextable code to paper.Rmd so easier to change to kable if needed.

@@

```{r label="intercept-table"}
tar_read(intercept_table) %>% set_caption(ci_cap, style = "Image Caption")
```

@@

```{r label="results-table"}
tar_read(results_table) %>% set_caption(result_cap, style = "Image Caption")
```

>>>>

```{r}
withr::with_dir(here::here(), {
  targets::tar_load(c(
    intercept_df,
    results_df
  ))
})
flextable::set_flextable_defaults(font.family = "Cambria", font.size = 10)
```

@@

```{r label="intercept-table"}
flextable(intercept_df) %>% 
  autofit() %>% 
  merge_v(j = 1) %>% 
  valign(j = 1, valign = "top") %>% 
  align(j = 3, align = "right", part = "all") %>% 
  bold(j = 3, i = c(3:6)) %>% 
  fix_border_issues() %>%
  set_caption(ci_cap, style = "Image Caption")
```

@@

```{r label="results-table"}
flextable(results_df) %>% 
  merge_v(j = c(2)) %>% 
  valign(j = c(2), valign = "top") %>% 
  align(j = c(5, 7), align = "right", part = "all") %>%
  colformat_double(j = c(3,6), digits = 2) %>% 
  fix_border_issues() %>% 
  flextable::compose(j = 3, part = "header",
                     value = as_paragraph("R", as_sup("2"))) %>% 
  flextable::compose(j = 4, i = c(4,9,15,20,26,31),
                     value = as_paragraph("s(log(size", as_sub("t"), "))")) %>%
  flextable::compose(j = 1, i = 12, 
                     value = as_paragraph("log(size", as_sub("t+1"), ")")) %>% 
  autofit() %>% 
  set_caption(result_cap, style = "Image Caption")
```
